---
title: "Math 237 Example Project"
---

:::{.disclaimer_block}

**Disclaimer**: This project formatting is adapted from the [Open Case Studies](https://opencasestudies.github.io){target="_blank"} project. The purpose of the Open Case Studies project is **to demonstrate the use of various data science methods, tools, and software in the context of messy, real-world data**. A given case study does not cover all aspects of the research process, is not claiming to be the most appropriate way to analyze a given data set, and should not be used in the context of making policy decisions without external consultation from scientific experts. 

:::

::: {.callout-note icon=false}
## Dr. Wynne's Note

At some points in the example project, you will see boxes like this. These boxes are not part of the example project, but indicate particular things to watch out for when you create your own project.

:::

## Motivation and Context

::: {.callout-note icon=false}
## Dr. Wynne's Note

This section describes what you are investigating in your project and why you are investigating it. You should provide enough contextual background and information that someone with a limited background can understand the broad outlines of the topic being investigated.

:::

```{r}
#| label: do this first
#| echo: false
#| message: false

here::i_am("math-237-example.qmd")
```

::: {.callout-note icon=false}
## Dr. Wynne's Note

There's an invisible chunk that uses `here::i_am` to indicate the location of this file relative to the rest of the project website. The option `echo: false` makes the code invisible and the option `message: false` prevents the "here() starts at..." message from displaying.

:::

## Main Objective

::: {.callout-note icon=false}
## Dr. Wynne's Note

This section should introduce your main question or objective in the context you described above.

:::


## Packages Used In This Analysis

::: {.callout-note icon=false}
## Dr. Wynne's Note

This section lists the packages used in the analysis. You should have a single chunk that loads the packages followed by a description you are using each package. The Open Case Studies project uses a tabular form, which I replicate below.

:::

```{r}
#| label: load packages
#| message: false
#| warning: false

library(here)
library(readr)
library(dplyr)
library(sf)
library(jsonlite)
```


::: {.callout-note icon=false}
## Dr. Wynne's Note

I included `message: false` and `warning: false` options in the chunk above so that package conflicts and similar issues aren't shown when loading the packages.

:::


 Package   | Use                                                                         
---------- |-------------
[here](https://github.com/jennybc/here_here)       | to easily load and save data
[readr](https://readr.tidyverse.org/)      | to import the CSV file data
[sf](https://r-spatial.github.io/sf/)   | to import and work with geojson files
[jsonlite](https://jeroen.r-universe.dev/jsonlite)  | to work with json files
[dplyr](https://dplyr.tidyverse.org/)      | to massage and summarize data

## Design and Data Collection

::: {.callout-note icon=false}
## Dr. Wynne's Note

This subsection should describe the data that you are using, the source of the data (including a link), and how the data was originally collected. At the end of the section you should import the data. 

:::

## Data Massaging

::: {.callout-note icon=false}
## Dr. Wynne's Note

This section should include most of your data wrangling. If you are creating training and test sets for predictive modeling, you should include that code in an appropriate place in this section.

:::

## Exploratory Data Analysis

::: {.callout-note icon=false}
## Dr. Wynne's Note

This section should include exploratory data analysis that is relevant to your objective.

:::

## Modeling

::: {.callout-note icon=false}
## Dr. Wynne's Note

If you are not building a model, you don't need this section. Otherwise, this section should include your predictive or inferential modeling.

:::

## Conclusion

::: {.callout-note icon=false}
## Dr. Wynne's Note

This section should include one or more graphs, figures or tables that summarize the primary finding with respect to your main objective. You should also have a paragraph describing that finding in the text and summarizing how you arrived at it.

:::

### Limitations

::: {.callout-note icon=false}
## Dr. Wynne's Note

This subsection should describe potential limitations of the conclusion and/or future work that someone might consider doing to expand on your analysis. Some limitations to discuss might include:

- What are the real-world consequences of using your data or models? What are the consequences of an incorrect conclusion or prediction?
- How appropriate was the data you used to answer your question? Consider aspects of validity (variables actually measure what you think they describe) and reliability (variable values would likely be similar if they were measured again).

:::

### Reflection

::: {.callout-note icon=false}
## Dr. Wynne's Note

You will be turning in a reflection privately on Canvas. However, you may want to include excerpts from that reflection here if you are comfortable making them public; for example, addressing:

- What did you learn about data science from this project?
- How did doing the data science increase your understanding of the domain you applied it to?

:::